Self Regulation Ontology Retest Analyses

### 2018-06-01 code/SRO_Retest_Analyses.Rmd
presentation prep

```{r}
tmp2 = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(ddm_task == 1, 
         overall_difference != "condition",
         rt_acc != "other") %>%
  drop_na() %>%
  left_join(rel_df[,c("dv", "icc", "spearman")], by = 'dv')

tmp2 %>%
  # filter(overall_difference == "overall") %>%
  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))))+
  geom_boxplot()+
  facet_wrap(~factor(overall_difference, levels=c("overall", "difference"), labels=c("Overall", "Difference")))+
  theme_bw()+
  ylab("ICC")+
  xlab("")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom',
        legend.text = element_text(size=16),
        strip.text = element_text(size=16),
        axis.text = element_text(size = 16),
        text = element_text(size=16))+
  guides(fill = guide_legend(ncol = 2))+
  scale_fill_discrete(breaks=c("Drift Rate", "Threshold", "Non-decision", "Response Time", "Accuracy"))+
  ylim(-0.4, 1)

>>>>

```{r}
tmp2 = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(ddm_task == 1, 
         overall_difference != "condition",
         rt_acc != "other",
         raw_fit != "hddm") %>%
  drop_na() %>%
  left_join(rel_df[,c("dv", "icc", "spearman")], by = 'dv')

tmp2 %>%
  # filter(overall_difference == "overall") %>%
  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))))+
  geom_boxplot()+
  facet_wrap(~factor(overall_difference, levels=c("overall", "difference"), labels=c("Overall (all trials)", "Difference (contrasting conditions)")))+
  theme_bw()+
  ylab("ICC")+
  xlab("")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom',
        legend.text = element_text(size=16),
        strip.text = element_text(size=16),
        axis.text = element_text(size = 16),
        text = element_text(size=16))+
  guides(fill = guide_legend(ncol = 2))+
  scale_fill_discrete(breaks=c("Drift Rate", "Threshold", "Non-decision", "Response Time", "Accuracy"))+
  ylim(-0.4, 1)
